Glasshouse experiment

### 2018-02-19 experiment_info.Rmd
.

---
title: "Untitled"
output: html_document
---
# Intro

@@

The study was done with x species where all the species where consider focal species from xxx to xxx at University of New England. The rooms where temperature controlled with temperature between xxx at day time to xxx at nigth time.

@@

>>>>

---
title: "Glasshouse experiment"
output: html_document
---
# Intro

@@

The study was done with x species (table 1) where all the species where consider focal species from xxx to xxx at University of New England. The rooms where temperature controlled with temperature between xxx at day time to xxx at nigth time.

Flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick. Had-pollination was realized with 3-4 gentle touches on the surface of the stigma. The mixes of pollen were realized based on the pollen counts on an eppendorf. Pollen on anthers was counted through Neubaeur chamber.

@@

```{r}

```
